---
title: "nkollibo_2"
author: "Niharika Kolliboyana"
date: "09-24-2023"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The below decision variables are:

For the quantities produced at Plant 1(P1):

L1: L1 is the no.of units of the Large size product

M1: M1 is the no.of units of the Medium size product

S1: S1 is the no.of units of the Small size product

For the quantities produced at Plant 2(P2):

L2: L2 is the no.of units of the Large size product

M2: M2 is the no.of units of the Medium size product

S2: S2 is the no.of units of the Small size product

For the quantities produced at Plant 3(P3):

L3: L3 is the no.of units of the Large size product

M3: M3 is the no.of units of the Medium size product

S3: S3 is the no.of units of the Small size product

**Formulation of LP problem**
$$ \text{Objective function is Zmax} = 420(L_1+L_2+L_3)+360(M_1+M_2+M_3)+300(S_1+S_2+S_3)$$
$$ \text{Expanding the objective function Zmax}= 420L_1 + 360M_1 + 300S_1 + 420L_2 + 360M_2 + 300S_2 + 420L_3 + 360M_3 + 300S_3 $$
subject to
$$L_1+M_1+S_1\le750$$
$$L_2+M_2+S_2\le900$$
$$L_3+M_3+S_3\le450 $$
$$20L_1+15M_1+12S_1\le13000$$
$$20L_2+15M_2+12S_2\le12000$$
$$20L_3+15M_3+12S_3\le5000$$
$$L_1+L_2+L_3\le900$$
$$M_1+M_2+M_3\le1200$$
$$S_1+S_2+S_3\le750$$
The non-negativity constraints
$$L_1, L_2, L_3, M_1, M_2, M_3, S_1, S_2, S_3\ge0 $$
**The above LP problem constraints can now be written as**
$$L_1+M_1+S_1+0L_2+0M_2+0S_2+0L_3+0M_3+0S_3\le750$$
$$0L_1+0M_1+0S_1+L_2+M_2+S_2+0L_3+0M_3+0S_3\le900$$
$$0L_1+0M_1+0S_1+0L_2+0M_2+0S_2+L_3+M_3+S_3\le450$$
$$20L_1+15M_1+12S_1+0L_2+0M_2+0S_2+0L_3+0M_3+0S_3\le13000$$
$$0L_1+0M_1+0S_1+20L_2+15M_2+12S_2+0L_3+0M_3+0S_3\le12000$$
$$0L_1+0M_1+0S_1+0L_2+0M_2+0S_2+20L_3+15M_3+12S_3\le5000$$
$$L_1+0M_1+0S_1+L_2+0M_2+0S_2+L_3+0M_3+0S_3\le900$$
$$0L_1+M_1+0S_1+0L_2+M_2+0S_2+0L_3+M_3+0S_3\le1200$$
$$0L_1+0M_1+S_1+0L_2+0M_2+S_2+0L_3+0M_3+S_3\le750$$


```{r}

library(lpSolve)

obj_fun<-c(420,360,300,420,360,300,420,360,300)
#Objective function

#Constraints
con_fun<-matrix(c(1, 1, 1, 0, 0, 0, 0, 0, 0,
                0, 0, 0, 1, 1, 1, 0, 0, 0,
                0, 0, 0, 0, 0, 0, 1, 1, 1,
                20, 15, 12, 0, 0, 0, 0, 0, 0,
                0, 0, 0, 20, 15, 12, 0, 0, 0,
                0, 0, 0, 0, 0, 0, 20, 15, 12,
                1, 0, 0, 1, 0, 0, 1, 0, 0,
                0, 1, 0, 0, 1, 0, 0, 1, 0,
                0, 0, 1, 0, 0, 1, 0, 0, 1),nrow = 9,byrow = TRUE)

#Direction of inequality constraints
dir_fun<-c("<=","<=","<=","<=","<=","<=","<=","<=","<=")

#Right hand side coefficients
rhs_fun<-c(750,900,450,13000,12000,5000,900,1200,750)


#objective value(Zmax)
lp('max',obj_fun, con_fun, dir_fun, rhs_fun)

#Values of the variables
lp_solution <- lp('max',obj_fun, con_fun, dir_fun, rhs_fun)$solution
# Extract solution values
production_plant <- lp_solution
# Format,print the production plan for each plant
for (plant in 1:3) {
  start_idx <- (plant - 1) * 3 + 1
  end_idx <- start_idx + 2
  plant_production <- production_plant[start_idx:end_idx]
  cat(sprintf("Plant %d:\n", plant))
  cat(sprintf("  Large: %f units\n", plant_production[1]))
  cat(sprintf("  Medium: %f units\n", plant_production[2]))
  cat(sprintf("  Small: %f units\n\n", plant_production[3]))
}



```